The pollination trade-off

### 2018-11-28 paper/manuscript.Rmd
Put figures of question two together in the manuscript

```{r fig-average-qual-quant, fig.height=1.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination. Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.). Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets."}
# height1 <- 1.25
# height2 <- 1.65
# pdf(width = 3.25 * 2, height = 1.29)
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
width_imp <- 6.5/3
mult <- 2.125
width_coef_1 <- (6.5 - width_imp) / (1 + mult)
width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
cowplot::plot_grid(
  fig_var_importance[[1]],
  fig_var_importance[[2]],
  fig_coef_avg[[1]],
  fig_coef_avg[[2]],
  ncol = 4, 
  rel_widths = c(width_imp/2, width_imp/2,width_coef_1, width_coef_2), 
  align = "h"
  )
# dev.off()
```

>>>>

By examining the AICc scores of a set of linear mixed effect models, we found that the visit efficay and the plants abbundance were the most important ecological variables predicting the amount of conspecific and heterospecific pollen deposited in the plant stigmas (Figure \@ref(fig:fig-average-qual-quant)a). 
The plants functional originality had an intermediate importance, while, surprisingly, the number of shared pollinators was comparatively less unimportant as it was only included in models with relatively large AICc values.

```{r fig-average-qual-quant, fig.height= 2.29, fig.width=6.5, fig.cap="Mean relative effect of ecological variables on the quantity and quality of pollination. Results are shown for values calculated with both the absolute gain in pollen density (abs.) and the gain relative to selfing (rel.). Bootstrap confidence intervals of the mean (at the 0.05 level) are shown in square brackets."}
height1 <- 1
height2 <- 1.29
# pdf(width = 3.25 * 2, height = sum(c(height1, height2)))
# fig_coef_avg <- plot_coefficient_averages(coefficient_averages, variable_importance)
width_imp <- 6.5/5*2
mult <- 2.355 # for 2/3 is 2.125, for 3/5 is 2.355
width_coef_1 <- (6.5 - width_imp) / (1 + mult)
width_coef_2 <- 5.6 - width_imp - width_coef_1
# fig_var_importance <- plot_variable_importance(variable_importance)
drake::loadd(fig_var_importance)
drake::loadd(fig_coef_avg)
drake::loadd(fig_coefficient_averages)

left_top <- cowplot::plot_grid(
  fig_var_importance[[1]],
  fig_var_importance[[2]],
  ncol = 2, 
  align = "h"
)

left_bottom <- cowplot::plot_grid(
  fig_coef_avg[[1]],
  fig_coef_avg[[2]],
  rel_widths = c(width_coef_1, width_coef_2), 
  align = "h"
)

left <- cowplot::plot_grid(
  left_top, 
  left_bottom, 
  ncol = 1, 
  rel_heights = c(height1, height2)
)

cowplot::plot_grid(
  left,
  fig_coefficient_averages, 
  ncol = 2,
  rel_widths = c(sum(c(width_coef_1, width_coef_2)), width_imp)
)
# dev.off()
```
